Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2020-01-18 ms.tex
showing the offsets along the dispersion direction.
showing LW + SW shifts simultaneously, which agree closely

	JWST's NIRCam instrument has very lower rates of persistence (<1 DN/sec) at 100 seconds after saturation, so it is expected that charge trapping will be a minor concern for JWST's HgCdTe detectors.

@@

We also analyze the spectroscopic time series for the OTIS grism time series.
The extracted spectrum and dynamic spectrum (how it varies in time) can be seen in Figure \ref{fig:otisLWdynSpec}.
Flat fielding is important for removing the imprint of the crosshatch pattern, as visible in Figure \ref{fig:otisLWflatVsNoFlat}.

@@

>>>>

	JWST's NIRCam instrument has very lower rates of persistence ($<$1 DN/sec) at 100 seconds after saturation, so it is expected that charge trapping will be a minor concern for JWST's HgCdTe detectors.

@@

We also analyze the spectroscopic time series for the OTIS grism time series.
The extracted spectrum and dynamic spectrum (how each wavelength varies in time) can be seen in Figure \ref{fig:otisLWdynSpec}.
Flat fielding is important for removing the imprint of the crosshatch pattern, as visible in Figure \ref{fig:otisLWflatVsNoFlat}.

@@

\begin{figure*}
\gridline{\fig{spec_offsets_o9LEDwf322w2Flat_NRCN83-256-O9LW.pdf}{0.49\textwidth}{}}
\caption{The position variations along the dispersion direction for this time series test are two orders of magnitude larger than expectation for flight.
}\label{fig:otisWavebinTSeries}
\end{figure*}

\subsection{Using SW centroid for LW grism}

We attempt to use the centroids form the SW imaging as input for a broadband grism aperture.
This potentially provides a way to input centroid information without cross-correlating a spectrum.
However, the SW centroids add more noise to the photometry as seen in Figure \ref{fig:otisLWSWtserShift}.
\textcolor{red}{\bf Did I properly multiply shifts by -0.5?}
